\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-20 paper/subdocuments/results.Rnw
minor changes plot options

<<different_ginis>>=
df$G_reink[df$G_reink==1]<-NA
df$G_taxed[df$G_taxed==1]<-NA
library(reshape)
dflong <- melt(df[,c("G_steink","G_reink","G_taxed","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("taxable income","income before deductions","taxable income after tax")
ggplot(dflong[dflong$kanton=="CH",], aes(x=steuerperiode,y=Gini,colour=Type))+geom_line(size=1)+theme_bw()+xlab("tax period")
ggplot(dflong, aes(x=steuerperiode,y=Gini,colour=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")
@

@@

@@

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

>>>>

<<different_ginis>>=
df$G_reink[df$G_reink==1]<-NA
df$G_taxed[df$G_taxed==1]<-NA
library(reshape)
dflong <- melt(df[,c("G_steink","G_reink","G_taxed","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("taxable income","income before deductions","taxable income after tax")
ggplot(dflong[dflong$kanton=="CH",], aes(x=steuerperiode,y=Gini,shape=Type))+
  scale_y_continuous(limits=c(0.18,0.4))+
  scale_x_continuous(limits=c(1982,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=Type),size=3)+
  geom_line(data=dflong[dflong$kanton=="CH",],aes(linetype=Type))+
  theme_bw()+
  xlab("tax period")
#ggplot(dflong, aes(x=steuerperiode,y=Gini,colour=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")
@

@@

% Wollen wir das ?berhaupt machen?

@@

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
#normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)
